### 2016-09-07 notions.tex
no message

>>>>

In this section we specialize to the case of set-membership data structures, and
focus on sets rather than multisets.
Before continuing, it will be useful to define a notion of ``point-wise min-entropy.''
Let ${\cal D}$ be
a distribution on sets over some universe ${\cal X}$. Then the \emph{point-wise
min-entropy} of ${\cal D}$ is defined as
\[H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S].\]
